Structured Synchronous Reactive Programming for Game Development \\ \Large{Case Study: On Rewriting Pingus from C++ to \CEU}

### 2017-05-28 paper.tex
(+) abstract

\abstract{TODO.

\smallskip

>>>>

\abstract{
We present a case study of rewriting the video game Pingus from C++ to \CEU, a
structured synchronous reactive programming language.
%
\CEU supports structured primitives that eliminates callbacks, letting
programmers write code in direct and sequential style, which help describing
complex control-flow relationships in the game logic more concisely.
%
We demonstrate gains in productivity for six behaviors in the game logic of
Pingus with an in-depth qualitative analysis of the proposed solutions in \CEU
in comparison to the original implementations in C++.
%
We also categorize the behaviors in four recurrent control-flow patterns that
likely apply to other games.
\smallskip
